---
title: "Rail Trail t Test"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(mosaic)
library(reshape2)
library(plotly)
library(pander)
```

<!-- Instructions

1. Use the RailTrail dataset in R to come up with a question that can be answered with a t Test. 

2. Establish why the question is interesting and rephrase the question using a statistical "null" and "alternative" hypothesis. (Hint, see the "Math 325 Notebook -> R Help -> R-Markdown Hints" page of your textbook for instructions on how to write mathematical hypotheses.)

3. Clearly answer your question using statistics. Be sure to compute a p-value and provide supporting numerical and graphical summaries.

For details about the RailTrail dataset type the command:
  > ?RailTrail 
into your Console and study the help file that appears. Also, if you want extra information, browse this document that has images and further details:
http://www.northamptonma.gov/DocumentCenter/View/5244   


Note: you can create "groups" from the data in many ways. For example, you can create a variable in your RailTrail dataset that is called "rain" and has categories of "yes" and "no" with the code:

-->

```{r}
railtrail <- RailTrail %>% 
  mutate(
    Weekday = case_when(
      dayType == "weekday" ~ 1,
      TRUE                 ~ 0
    ),
    Weekend = case_when(
      dayType == "weekend" ~ 1,
      TRUE                 ~ 0
    )
  ) %>% 
  select(-c(weekday, dayType))
```

## Introduction
The following analysis was done with the Rail Trail data set. Below is a description of this data set from its mosaicData help page.

<div style="padding-left:50px;">
The Pioneer Valley Planning Commission (PVPC) collected data north of Chestnut Street in Florence, MA for ninety days from April 5, 2005 to November 15, 2005. Data collectors set up a laser sensor, with breaks in the laser beam recording when a rail-trail user passed the data collection station.

There is a potential for error when two users trigger the infrared beam at exactly the same time since the counter would only logs one of the crossings. The collectors left the motion detector out during the winter, but because the counter drops data when the temperature falls below 14 degrees Fahrenheit, there is no data for the cold winter months.
</div>


## Hypotheses:

I hypothesize the temperature of the day can explain the volume of visitors, or in other words, there is a correlation between the high temperatures of each day and the volume of visitors. For this test, I will be using the Student's t-Test.

<div style="padding-left:15px;">
$H_0: \mu_1 - \mu_2 = 0$ </br>
$H_a: \mu_1 - \mu_2 \neq 0$
</div>

## Analysis


### Scatter Plot and Trend Line
Here is a scatter plot of the volume and high temperature of each day data was collected. I included a trendline to show the trend of the data points. You can see there seems to be a pattern, with the volume of visitors increasing with the high temperatures. Let's perform a test in search of some evidence.

```{r message=FALSE, warning=FALSE}
# Faceted Density Plot
railtrail %>% 
  ggplot(aes(x = volume, y = hightemp)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_y_continuous(breaks = seq(40,100,by = 10)) +
  scale_x_continuous(breaks = seq(100,800,by = 100)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    title = "Trend line shows volume of visitors increases as temperatures rise.",
    x = "Volume of visitors",
    y = "High temperature"
  )
```


### Student's t-Test
Here are the results of the Student's t-Test.

```{r}
# Student's t-Test
pander(t.test(railtrail$volume, railtrail$hightemp, mu = 0, alternative = "two.sided"))
```

Since the t-value is greater than the p-value, there is sufficient evidence to reject the null hypothesis. This suggests that there is a correlation between the high temperatures of each day and the volume of visitors. 

### Pearson's Correlation Coefficient
[Pearson's Correlation Coefficient](https://www.statisticshowto.datasciencecentral.com/probability-and-statistics/correlation-coefficient-formula/) is a statistical measurement of the strength of a relationship. The number could be positive or negative, depending on the type of relationship between variables. When I say "relationship"", I refer to how the change in one variable can cause a change in another. Below, I constructed a correlation matrix which shows how the variables in the Rail Trail data set relates to each other.

```{r message=FALSE, warning=FALSE}
# Step 1
cormat_trail <- round(cor(railtrail),2)

# Step 2
melted_cormat <- melt(cormat_trail)

# Step 3
get_upper_tri <- function(data_set){
  data_set[lower.tri(data_set)] <- NA
  return(data_set)
}

upper_tri_trai <- get_upper_tri(cormat_trail)
melted_upper_tri <- melt(upper_tri_trai, na.rm = TRUE)

# Step 4
ggplot(data = melted_upper_tri, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") + 
  geom_text(aes(label = value), color = "black") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1), space = "lab",
                       name = "Pearson\nCorrelation") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.justification = c(1, 0),
        legend.position = c(0.50, 0.75),
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                               title.position = "top", title.hjust = 0.5)) +
  coord_fixed() +
  labs(
    title = "There is a strong positive correlation between \nhigh temperatures and volume of park visitors.",
    x = "",
    y = ""
  )
```

As you can see, there seems to be a positive correlation between high temperatures and volume of visitors. The correlation seems to be high in comparison to some of the other variables.

## Conclusion
The Student's t-Test provided sufficient evidence to reject the null hypothesis, which leaves me to conclude that there is a correlation between high temperatures and volume of visitors. 

</br></br></br></br>