---
title: "Analysis 1 - Stephanie"
author: "Daniel Lopez"
date: "September 20, 2018"
output: 
  html_document:
    theme: paper
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaflet)
library(ggrepel)
library(plotly)

Rent <- read_csv("../../Data/Rent.csv") %>% 
  na.omit() %>% 
  filter(Gender == "F") %>% 
  mutate(
    Size = case_when(
      Capacity < 50 ~ "Small",
      Capacity < 100 ~ "Medium",
      TRUE ~ "Large"
    )
  )
```

## Background

Stephanie is a student that will be starting school at BYU-Idaho next semester. Suppose she sent you the following email.

"Hi. My name is Stephanie. I would like to learn about what housing options I have for living at BYU-Idaho next semester. It will be my first semester there, so I would like to find something that is close to campus and around $300 a month in rent. I'm not too picky on roomates, but I would like somewhere that has a lot of people around so I can get to know as many people as possible. Thanks in advance!"

## Response

Dear Stephanie, 
I found a few good housing options for you that are affordable and close to campus and other students. I created a graph that compares each BYU-I approved housing complex by proximity to campus and price per semester. I also adjusted the size of each point on the graph to reflect its housing capacity. The graph is intereactive, which means you can zoom in and out, as well as hover over each point to see which housing unit it represents. Please take a look below.

```{r, fig.align='center', message=FALSE, warning=FALSE}
### Distance ~ Price ~ Gender
Rent %>% plot_ly(x = ~MilesToCampus,
                 y = ~Price,
                 size = ~Capacity,
                 color = ~Size,
                 text = ~paste("Apartment: ", Apartment,
                               "<br>Price: ", Price,
                               "<br>Capacity: ", Capacity))

CheapNClose <- 
  Rent %>% 
  filter(Price < quantile(Rent$Price, 0.30)) %>% 
  filter(MilesToCampus < quantile(Rent$MilesToCampus, 0.30))

```

### The Map
I added a map of Rexburg below with markers for each student approved housing complex.I thought you would like to see where each housing unit is in relation to the campus and other popular spots in Rexburg. This graphic is also interactive, so you can zoom in and out as well as click on any marker to see the housing unit's name, price and other information. 

```{r, fig.align='center', message=FALSE}
### Leaflet Map
getColor <- function(Rent) {
  sapply(Rent$Price, function(Price) {
    if(Price <= 1000) {
      "green"
    } else if(Price <= 1200) {
      "yellow"
    } else {
      "red"
    } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(Rent)
)

leaflet(options = leafletOptions()) %>% 
  addTiles() %>% 
  addLabelOnlyMarkers(data = CheapNClose,
             label = ~Apartment,
             labelOptions = labelOptions(noHide = T)) %>%
  addAwesomeMarkers(data = Rent,
                    lng = ~Longitude,
                    lat = ~Latitude,
                    icon = icons,
                    popup = ~paste0("Name: ", Apartment, "<br/>",
                                    "Gender: ", Gender, "<br/>",
                                    "Address: ", Address, "<br/>",
                                    "Phone: ", Phone, "<br/>",
                                    "Shared Room: ", Price, "<br/>",
                                    "Private Room: ", PrivateRoomPrice, "<br/>",
                                    "Deposit: ", Deposit, "<br/>"))
```

## Conclusion
There are three housing unites who's labels aren't hidden. These are my top reccomendations based on price and proximity to campus. I think the best choice for you would be Allen's Sunrise Village - Women. It has a capacity over 100, it's accross the street from the campus, and just down the block from popular places to eat in Rexburg. Best of all, the price is affordable at just above $300 per month.

<br><br><br>